---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures",
  out.width = "100%"
)
```

# TMEscore

### 1.Introduction
TME infiltration patterns were determined and systematically correlated with TME cell phenotypes, genomic traits, and patient clinicopathological features to establish the [TMEscore](https://cancerimmunolres.aacrjournals.org/content/7/5/737):Tumor Microenvironment Characterization in Gastric Cancer Identifies Prognostic and Immunotherapeutically Relevant Gene Signatures.


TMEscore is an R package to perform tumor microenvironment analysis. 
 Main advantages:
1. Provides functionality to calculate Tumor microenvironment (TME) score (PCA or z-score)
2. Functions to visualize TME data.
3. Identify TME relevant mutations.

### 2.Installation
The package is not yet on CRAN. You can install from Github:
```{r}
# install.packages("devtools")
if (!requireNamespace("TMEscore", quietly = TRUE))
  devtools::install_github("DongqiangZeng0808/TMEscore")
```

### 3.Usage
Main documentation is on the `tmescore` function in the package:

```{r}
library('TMEscore')
```

Example
```{r}
tmescore<-tmescore(eset = eset_stad, #expression data
                   pdata = pdata_stad, #phenotype data
                   method = "PCA", #default
                   classify = T) #if true, survival data must be provided in pdata
head(tmescore)
```
```{r,fig.height=6, fig.width= 8}
#remove observation with missing value
tmescore<-tmescore[!is.na(tmescore$subtype),]

p<-ggplot(tmescore,aes(x= subtype,y=TMEscore,fill=subtype))+
  geom_boxplot(notch = F,outlier.shape = 1,outlier.size = 0.5)+
  scale_fill_manual(values= c('#374E55FF', '#DF8F44FF', '#00A1D5FF', '#B24745FF'))

comparision<-combn(unique(as.character(tmescore$subtype)), 2, simplify=F)

p+theme_light()+stat_compare_means(comparisons = comparision,size=6)+stat_compare_means(size=6)
```

### Citation
If you use TMEscore in published research, please cite: [Tumor microenvironment characterization in gastric cancer identifies prognostic and imunotherapeutically relevant gene signatures](https://cancerimmunolres.aacrjournals.org/content/7/5/737). Cancer Immunology Research, 2019, 7(5), 737-750. DOI: 10.1158/2326-6066.CIR-18-0436, PMID: 30842092
and 
[Tumor microenvironment evaluation promotes precise checkpoint immunotherapy of advanced gastric cancer](https://jitc.bmj.com/content/9/8/e002467). 
Journal for ImmunoTherapy of Cancer, 2021, 9(8), e002467. DOI: 10.1136/jitc-2021-002467, PMID: 34376552

### Contact
E-mail any questions to dongqiangzeng0808@gmail.com
